Choose a License

### 2024-11-28 choose_license.qmd
Explain output exception

In most cases, the output of software, like images or tables, does not depend on the software's license. Therefore, if you use an R package under a copyleft license to create a figure, you are likely the copyright owner. However, if the output is based on data, it can be considered a derivative work and the license of the data also applies. For example, maps may be considered as a derivative of the geographic data they are based on.

>>>>

In most cases, the output of software, like images or tables, does not depend on the software's license.^[The exception is when the software is part of the output [see @apsillers2019].] Therefore, if you use an R package under a copyleft license to create a figure, you are likely the copyright owner. However, if the output is based on data, it can be considered a derivative work of the data and the license of the data also applies. For example, maps may be considered as a derivative of the geographic data they are based on.
